Generality in food webs scales with species richness, not latitude

### 2015-02-03 manuscript/latitudepaper.tex
ran through the discussion again too.

The tendency of food-web structure to exhibit scaling relationships with both
species richness and connectance has been well-established \citep{}. As
species richness in particular is also known to vary systematically over
latitude \citep{}, intuitively one might suspect that any relationship
between food-web properties such as generality might be due to the latitudinal
gradient in species richness. In this dataset, however, we did not find
overall latitudinal gradients in species richness, links per species, 
generality, or vulnerability. This fact notwithstanding, latitude did affect the
scaling relationships between species richness and the other network properties.

The lack of latitudinal gradients in food-web properties in this dataset contrasts
strongly with other studies which have found consistent variation in species richness,
[[other properties]] \citep{}. As numbers of species and links included in a food web
vary strongly with sampling effort as well as with the underlying diversity of the study
area, it is possible that the lack of latitudinal trends here is a result of researchers
tending to expend similar amounts of sampling effort across studies. This could result in
food webs describing species-rich tropical communities omitting more species and links
than species-poor arctic communities. While unusual, the lack of association between species richness
and latitude in any ecosystem type nevertheless means that any effect of latitude on scaling relationships
between species richness and other properties is not being driven by underlying variation in
species richness, allowing us to more clearly assess effects of latitude on scaling.

Our scaling results provide only equivocal support for the niche-breadth hypothesis.
In particular, scaling relationships between species richness and links per species,
generality, or vulnerability strengthened with increasing latitude for lake and stream
food webs but did not vary significantly with latitude in estuarine, terrestrial, and
marine communities. In lakes and streams, the niche hypothesis' proposal that niches
are narrower in the tropics fits the observed scaling patterns. The increase in links
per species as food-web size increases is much slower in low-latitude communities than
in their high-latitude counterparts. From this, we can infer a higher proportion of
specialists with few predators in tropical communities. This echos earlier research [[details]]
\citep{}. In contrast, temperate and polar communities appear to contain more generalist
species. As food webs are generally aggregated over space and time, the stronger
increase in links per species with species richness could be driven by species switching
between more prey species that are only intermittently available in areas with highly
variable climates.

@@

[[something catchy to sum up]]

>>>>

The tendency of food-web structure to exhibit scaling relationships with
species richness has been well-established \citep{Dunne2004,Riede2010}. As
species richness in particular is also known to vary systematically over
latitude \citep{}, intuitively one might suspect that any relationship
between food-web properties such as generality might be due to the latitudinal
gradient in species richness. In this dataset, however, we did not find
overall latitudinal gradients in species richness, links per species, 
generality, or vulnerability.

The lack of latitudinal gradients in food-web properties in this dataset contrasts
strongly with other studies which have found consistent variation in species richness,
[[other properties]] \citep{}. As numbers of species and links included in a food web
vary strongly with sampling effort as well as with the underlying diversity of the study
area, it is possible that the lack of latitudinal trends here is a result of researchers
tending to expend similar amounts of sampling effort across studies. This could result in
food webs describing species-rich tropical communities omitting more species and links
than species-poor arctic communities. In addition, it is worth noting that gradients in
species richness are generally measured for a single taxonomic group at a time~\citep{}.
It is possible that these taxa are not well-represented in our food webs and that the
dominant taxa in them do not have an underlying latitudinal gradient in richness. In
either case, the lack of association between species richness
and latitude in any ecosystem type nevertheless means that any effect of latitude on scaling relationships
between species richness and other properties is not being driven by underlying variation in
species richness, allowing us to more clearly assess effects of latitude on scaling.

These effects varied strongly across ecosystem types. In marine and terrestrial food webs,
scaling of links per species, generality, and vulnerability was not strongly affected by
latitude. This is consistent with the idea that species' niche breadths do not vary systematically
with temperature and productivity but that the niche space might be larger in species-rich communities
~\citep{Davies2007}. In contrast, scaling in of lake, estuarine, and stream was generally stronger
towards the poles. This means that species in tropical communities gain fewer additional feeding links
per additional species in the web, supporting the hypothesis that greater stability in the tropics
leads to narrower niches~\citep{Brown2004} and a higher proportion of specialists~\citep{}. As food webs
are generally aggregated in space and time, the greater increase in links in high latitude stream, 
estuarine, and lake food webs might reflect prey switching as different food sources become
available~\citep{}.

@@

Our results were consistent with the latitude-niche breadth hypothesis, but only in certain ecosystem
types. This suggests that different types of food webs respond differently to differences in climate
driven by latitudinal gradients. [[A sentence or two explaining why this is important.]]
